---
title: Central Limit Theorem
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Definition

The random variable $X$ is said to have a standard normal distribution if it has density
$$
\begin{aligned}
\phi({x}) = \frac{1}{\sqrt{2 \pi}} e^{- \frac{1}{2} x^2}
\end{aligned}
$$

### Theorem
Let $X_1,...,X_n$ be a sequence of independent and identically distributed random variables with mean $\mu$ and variance $\sigma^2$. Let $\bar{X} = {\frac{1}{n}} {\sum\nolimits_{i=1}^{n}} {X_i}$. Then

$$
\begin{aligned}
{P} \, ({\sqrt{n}} \, {\frac{\bar{X} - {\mu}}{\sigma}} \, {\leq} \, {x}) \, {\rightarrow} \, {\Phi} ({x})
\end{aligned}
$$

where $\Phi ({x}) = \int_{-\infty}^{x} \phi (t)dt$.

As an illustration we do the following: we generate 100 observations from a uniform distribution on [0,1] and find its sample mean. We know that if $U \sim U[0,1]$ we have $\mu = \frac{1}{2}$ and $\sigma^2 = \frac{1}{12}$. So

$$
\begin{aligned}
{Z_1} = \sqrt{n} \, \frac{\bar{X} - \mu}{\sigma} = \\
\sqrt{100} \, \frac{\bar{X} - 1/2}{\sqrt{1/12}} = \\
\sqrt{300} \, \left(2 \bar{X} - 1\right)
\end{aligned}
$$

now we repeat this 10000 times:

```{r}
z <- rep(0, 10000)
for(i in 1:10000) {
  x <- runif(100)
  z[i] <- sqrt(300)*(2*mean(x)-1)
}
```

Finally we can compare the relative frequencies with the theoretical probabilities for different values of $x$. For example  if $x = 1.5$ we find

```{r}
round(c(length(z[z<1.5])/10000, pnorm(1.5)), 4)
```

and so the difference is `r round(length(z[z<1.5])/10000,4)` - `r round(pnorm(1.5),4)` = `r round(length(z[z<1.5])/10000 - pnorm(1.5),4)`.



